Normalization

### 2022-02-10 reports/rmarkdown/01_data_pre_processing.Rmd
removing code not in use

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  organisation: Karolinska Institutet
  pi_mail: prin.cipal@ki.se
  pi_name: Prin Cipal
  project_title: Broliden_5325
  redmine_issue: '#5325'
  requester_mail: kristina.broliden@ki.se
  requester_name: Kristina Broliden
  staff_mail: supp.ortstaff@nbis.se
  staff_name: Supp Ortstaff
  staff_web: https://nbis.se/about/staff/supp-ortstaff/
---

@@

setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown")
```

#Load libraries and other scripts

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
library(igraph)
library(rafalib)
library(sva)
library(batchelor)
remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
library(niceRplots)
library(tidyverse)
})  })  })

@@

# Load metadata
dataset_names <- c("ASV_tissue_V3_B2.csv",   # Tissue, Boston run 2 (95 samples)
                     "ASV_tissue_V3_B1.csv", # Tissue, Boston run 1 (1 sample)
                     #"ASV_CVL_V2_B1.csv", # CVL V2, Boston run 1 (27 samples)
                     #"ASV_CVL_V2_B2.csv", # CVL V2, Boston run 2 (49 samples)
                     #"ASV_CVL_V2_S.csv",  # CVL V2, CTMR         (62 samples)
                     "ASV_CVL_V3_B1.csv") # CVL V3, Boston run 1 (111 samples)

@@

# make long format raw non agglom ASV files
# remove_from_CVL_V2 <- intersect(colnames(temp_[[5]]), colnames(temp_[[3]]))[-c(1:11)]
# names <- c("ASV_tissue_V3_Boston run2","ASV_tissue_V3_Boston run1", "ASV_CVL_V2_Boston run1", 
#                      "ASV_CVL_V2_Boston run2", "ASV_CVL_V2_Stockholm", "ASV_CVL_V3_Boston run 1") 
# ASV_long <- temp_ %>%
#   modify_at(., c("ASV_CVL_V2_C.csv"), ~select(.x, -any_of(remove_from_CVL_V2))) %>% 
#   map(., ~pivot_longer(.x, matches("^P\\d"), names_to = "ID", values_to = "Reads")) %>%
#   set_names(names ) %>%
#   bind_rows(., .id = "dataset") %>%
#   separate(., dataset, into=c(NA, "Sample_type", "Visit","Place_sequenced"), sep = "_", remove = F) %>% 
#   mutate(dataset = str_extract(.$dataset, "CVL_V\\d|tissue_V3")) %>% 
#   group_split(dataset, .keep=F) %>% set_names(c("tissue", "CVL_V2", "CVL_V3"))
# 
# saveRDS(ASV_long, paste0(PATH,"results/","ASV_all_data_long_format.RDS"))

@@

# datasets <- datasets[3] #in case you wanna test in 1 dataset

# Transform phyloseq data into normalized matricies ( log2[CP1K] )
# datasets <- lapply(datasets,function(x){
#     x <- t(log2( t(x) / colSums(x) * 1000 + 1))
# })
# lapply(datasets,dim)

@@

# Merging, renaming and correcting batch effects on datasets

@@

@@

>>>>

---
title: "Normalization"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
---

@@

#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown")
```

# Load libraries and other scripts

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
#remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
library(niceRplots)
library(tidyverse)
})  })  })

@@

dataset_names <- c("ASV_tissue_V3_B2.csv", # Tissue, Boston run 2 (95 samples)
                   "ASV_tissue_V3_B1.csv", # Tissue, Boston run 1 (1 sample)
                   #"ASV_CVL_V2_B1.csv",   # CVL V2, Boston run 1 (27 samples)
                   #"ASV_CVL_V2_B2.csv",   # CVL V2, Boston run 2 (49 samples)
                   #"ASV_CVL_V2_S.csv",    # CVL V2, CTMR         (62 samples)
                    "ASV_CVL_V3_B1.csv")   # CVL V3, Boston run 1 (111 samples)

@@

@@

@@

# Merging and renaming

@@

# normalize and save microbiome datasets

@@

# normalize and save trx datasets
